Something fancy...

### 2020-01-20 draft.tex
incomplete

\section{Introduction}

topological phases --- interacting and non-interacting

How to identify interesting phases?--- entanglement entropy, entanglement spectrum

>>>>

\section{Introduction}
Topological phases of matter have attracted more and more attention during the last decades, not the least because many more relevant systems have been realized experimentally. 
The early focus was mainly on \emph{topologically ordered} systems \cite{Wen}, where interaction effects are crucial for stabilizing the phase. 
The most notable examples are the fractional quantum Hall effect~\cite{} and quantum spin liquids~\cite{}. 
However, since 2005 \maria{?}~\cite{KaneMele, etc} the focus has shifted to non-interacting topological phases, which can be characterized in terms of topological invariants~\cite{}. 
Symmetries are often necessary to protect these topological phases, and determine which distinct topological phases can be realized for a given dimensionality.

XXX
How to identify interesting phases?--- entanglement entropy, entanglement spectrum
